Verification of Stencil Computations through Spatial Specifications

### 2016-07-07 paper.tex
edits

This paper considers the technical aspects of the language,
its semantics, inference, checking, and synthesis procedures.
We also evaluate our implementation on real scientific code 
used actively in research. Our case studies include the Unified Weather 
model used by the UK Met Office~\cite{um-website} ($\approx{}600\textit{kloc}$) and other
research-based numerical models, ranging from small to large.

@@

The product of two regions $r \texttt{*} r'$ specifies that an array
is read with neighbourhood indices drawn from the bounding box created
by the regions two regions $r$ and $r'$. For example, the following
code (defining a \emph{nine-point stencil}) has a specification given by the
product of two \texttt{centered} regions in each dimension:
%%
\begin{minted}[breakindent=2.9em]{fortran}
x = a(i, j)   + a(i-1, j)   + a(i+1, j)
y = a(i, j-1) + a(i-1, j-1) + a(i+1, j-1)
z = a(i, j+1) + a(i-1, j+1) + a(i+1, j+1)

!= stencil centered(depth=1, dim=1) * centered(depth=1, dim=2) :: a
b(i, j) = (x + y + z) / 9.0
\end{minted}
%%
This pattern is a common image convolution (for example
for edge detection). The specification ranges over the
values that flow the array subscript on the left-hand side,
and so ranges over the intermediate assignments to \term{x},
\term{y}, and \term{z}.

@@

\subsection{Note on the design}

The names ``forward'', ``backward'' and ``centered''
are inspired by standard terminology in numerical analysis
for the shape of discretisation schemes. For example,
the standard \emph{explicit method} for approximating
PDEs is known as the \emph{Forward Time, Centered Space} (FTCS)
scheme~\cite{dawson1991finite}. For
the one-dimensional heat equation, an FTCS discretisation
provides approximation code with the following stencil~\cite{recktenwald2004finite}:
%%
\begin{minted}{fortran}
do i=2, n-1
  u(i) = r*v(i-1) + r2*v(i) + r*v(i+1)
end do
\end{minted}
%%
where \texttt{r} and \texttt{r2} are constants.
A valid specification for this is:
%%
\begin{minted}{fortran}
!= stencil centered(depth=1, dim=1) :: v
\end{minted}
%%
Such a specification can be inferred, or can be inserted by a user
and checked against the code.

@@

Figure~\ref{fig:equations} lists the equational theory for
specifications which is defined by the binary relation $\equiv$
between region terms. Stencil declarations are considered
equal when they have the same modifiers and $\equiv$ equates
their regions, \ie{}:
\begin{align*}
(\textit{region} \equiv \textit{region'}) 
 \Rightarrow \quad\;\; & \texttt{stencil} \; [\textit{approx},] \; [\textit{mult},] \;
\textit{region} \\[-0.4em]
\quad \equiv \; & \texttt{stencil} \; [\textit{approx},] \;
            [\textit{mult},] \; \textit{region}'
\end{align*}
%
The equations of Figure~\ref{fig:equations} use abbreviations
\term{refl}, \term{fwd}, \term{bwd}, \term{cen}, and \irreflS{}
for \term{reflexive}, \term{forward}, \term{backward},
\term{centered}, and \irrefl{} respectively. Futhermore, the abbreviations include syntactic sugar
for quantifying over the abseence or presence of the \irrefl{}
attribute on region constants as a boolean. For example,
the syntactic sugar for \term{fwd} is defined:
%%
\begin{align*}
\hspace{-0.25em}
& \stenFwdSR{n}{d}{r}
\; := \; \\[-0.4em]
& \qquad \begin{cases}
\stenFwd{n}{d}{, \irrefl} & \;\;\textit{if} \;\, \neg \, r \\
\stenFwd{n}{d}{}  & \;\;\textit{if} \;\,  r
\end{cases} \\
\textit{or} \;\;
& \stenFwdS{n}{d} := \stenFwd{n}{d}{}
\end{align*}
%
and similarly for \term{bwd} and \term{cen}.

The equations reveal a partial semantics for stencil
specifications, which we briefly summarise.

@@

\begin{definition}
An \emph{index scheme} is a vector of size $n$ (an $n$-vector)
with values drawn from $\domainVal = \mathbb{Z} \cup \{\infty\}$.
Values in $\mathbb{Z}$ represent offsets
of a neighbourhood index (indexing
expressions of the form $i + a$ where $i$ is an induction variable
and $a$ is a constant offset, Def.\ref{def:neighbour},
p.\pageref{def:neighbour}). The additional value
$\infty$ represents any indexing behaviour--- it is a
wildcard.
Throughout $u, v, w$ range over index schemes and $u_i$ denotes
the $i^{th}$ element of $u$. We write $(\domainVal)^n$ for
the set of $n$-dimensional schemes.
\end{definition}

Indexing schemes give an abstract
representation of index expressions in the source language.
Our model represents the meaning of stencil specifications
as indexing schemes, which explain the range of possible
indexing behaviours allowed under the specification.
The relationship between indexing schemes and source language
terms is given precisely by the partial function, \textsf{schematic}, which
maps syntactic array-index terms to indexing schemes. This
operation is used by the inference
and the checking procedures.

\begin{definition}%[Schematic]
\label{def:schematic}
The partial function $\textsf{schematic}$ maps
source indexing terms $(e_1, .., e_n)$
to $n$-dimensional index schemes, defined:
%
\begin{align*}
\mathsf{schematic}(e_1, \ldots, e_n) & =
[\downarrow\!e_1 \ldots \downarrow\!e_n ]
\quad \textit{iff} \;\; \forall i . \downarrow\!e_i \neq \bot
\end{align*}
%
The $\downarrow$ operator is partial\footnote{We represent
  partiality in our signatures with the set $A + \bot$.} 
 $\downarrow : \textit{expr} \rightarrow (\domainVal + \bot)$
mapping individal indexing expressions to 
an indexing scheme component, defined:
%%
\begin{align*}
\downarrow\!e
 & =  \begin{cases}
a & e \equiv i + a \; \wedge \; \mathsf{neigh}(i + a) \\
-a & e \equiv i - a \; \wedge \; \mathsf{neigh}(i - a) \\
\infty & \textit{$\mathsf{IV}(e) = \emptyset$} \\
\bot   & \textit{otherwise}
\end{cases}
\end{align*}
%%
where $\mathsf{IV}(e)$ is the set of free induction variables
appearing in an expression, and $\neigh{}$ classifies expressions which
are constant offsets from an induction variable
(Defn.~\ref{def:neighbour}). In the third case,
if the expression is not a neighbourhood index but is not
a relative index either (\ie{}, not defined in terms
of an induction variable) then it is mapped to $\infty$, otherwise
$\downarrow\!e$ is undefined. The $\mathsf{schematic}$ function
is undefined if $\downarrow$ of any of its components $e_i$ is
undefined.

@@

\begin{figure}[t]
\vspace{-0.3em}
\hspace{-0.5em}
\begin{minipage}{0.16\linewidth}
\begin{align*}
\setlength{\arraycolsep}{0em}
\begin{array}{c}
\quad \\[0em]
\begin{tikzpicture}[scale=0.8]
%\draw[step=0.5cm,lightgray,very thin] (0.5,0.5) grid (2,2);
\node at (1.25,1.22) {\textnormal{\footnotesize{0,0}}};
\draw[thick] (1,1) rectangle (1.5,1.5);
\draw[thick] (1.5,1) rectangle (2,1.5);
\draw[thick] (1,0.5) rectangle (1.5,1);
\draw[thick] (0.5,1) rectangle (1,1.5);
\draw[thick] (1,1.5) rectangle (1.5,2);
\end{tikzpicture} \\[0em]
(a)
\end{array}
\end{align*}
\end{minipage} $\rightarrow$ \begin{minipage}{0.43\linewidth}
\begin{align*}
\setlength{\arraycolsep}{0em}
\begin{array}{c}
\begin{tikzpicture}[scale=0.72]
%\draw[step=0.5cm,lightgray,very thin] (0.5,0.5) grid (2,2);
%\node at (1.25,1.22) {\textnormal{\small{0,0}}};
\draw [black, thin] (0.35,0) to [round left paren ] (0.35,2);
\draw[thick] (0.5,1) rectangle (2,1.5);
\draw[thick] (1,0.40) rectangle (1.5,0.90);
\draw[thick] (1,1.60) rectangle (1.5,2.10);
\node at (2.3,1.22) {+};
\draw[thick] (3.8,1) rectangle (4.3,1.5);
\draw[thick] (2.6,1) rectangle (3.1,1.5);
\draw[thick] (3.2,0.5) rectangle (3.7,2);
\draw [black, thin] (4.4,0) to [round right paren ] (4.4,2);
\end{tikzpicture} \\[-0.5em] (b)
\end{array}
\end{align*}
\end{minipage}$\rightarrow$ \begin{minipage}{0.25\linewidth}
\begin{align*}
\setlength{\arraycolsep}{0em}
\begin{array}{c}
\begin{tikzpicture}[scale=0.72]
%\node at (1.25,1.22) {\textnormal{\small{0,0}}};
\draw [black, thin] (0.8,0) to [round left paren ] (0.8,2);
\draw[thick] (1,0.5) rectangle (1.5,2);
\node at (1.8,1.22) {+};
\draw[thick] (2.1,1) rectangle (3.6,1.5);
\draw [black, thin] (3.7,0) to [round right paren ] (3.7,2);
%\node at (2.75,1.22) {\textnormal{\small{0,0}}};
\end{tikzpicture} \\[-0.5em] (c)
\end{array}
\end{align*}
\end{minipage}
\caption{Illustration of grouping spans in
specification inference}
\label{fig:inference-steps-informal}
\vspace{-0.8em}
\end{figure}

@@

@@

\begin{figure}
\input{consistency.tex}
\caption{Consistency between a model and indexing schemes from a stencil computation}
\label{fig:consistency}
\vspace{-0.9em}
\end{figure}

@@

\begin{figure}[t]
  \centering
  %\subcaptionbox{\label{fig:jacobicorrect}}{\includegraphics[width=0.1\textwidth]{jacobi-correct.png}}
  %\subcaptionbox{}{\includegraphics[width=0.1\textwidth]{jacobi-incorrect1.png}}
  %\subcaptionbox{}{\includegraphics[width=0.1\textwidth]{jacobi-incorrect2.png}}
  %\subcaptionbox{}{\includegraphics[width=0.1\textwidth]{jacobi-incorrect3.png}}
  \subfigure[]{\label{fig:jacobicorrect}\includegraphics[width=0.1\textwidth]{jacobi-correct.png}}
  \subfigure[]{\includegraphics[width=0.1\textwidth]{jacobi-incorrect1.png}}
  \subfigure[]{\includegraphics[width=0.1\textwidth]{jacobi-incorrect2.png}}
  \subfigure[]{\includegraphics[width=0.1\textwidth]{jacobi-incorrect3.png}}
  \caption{Greyscale output of several perturbations of a Jacobi
    iteration program. The correct output is shown in
    \subref{fig:jacobicorrect}.}
  \label{fig:jacobi}
  \vspace{-0.7em}
\end{figure}

@@

There are 48 possible errors of this type of which we found only 6 were not 
detected by the specification checking. The reason is that the inferred
specification describes a family of access patterns. Some offset errors
produce a stencil computation that belongs to the same family and goes
undetected.

One of the reasons this specification can catch many offset errors is that it is
a \texttt{readOnce} specification. This prevents offset errors leading to
duplicate access patterns be caught even if the resulting set of accesses are
part of the same family.
% /um/trunk/src/atmosphere/diffusion_and_filtering/turb_smagorinsky.F90
% Tried introducing indexing errors replacing one of the indices of cx_rho_instance with -1,0,+1
% 42 cases were caught
% 6 cases were not caught
\section{Related work}
\label{sec:discussion}

@@

In this paper, we described an abstract specification language 
for the access pattern of a stencil computation. Compared with the
related work (discussed above), our language is novel in that it does
not aim to replicate indexing in the specification, but instead
provides a set of abstract spatial combinators which capture a large number
of common patterns.

We evaluated our approach by implementing the stencil inference and
checking procedure ontop of CamFort, an open-source analysis
tool\footnote{\url{https://github.com/camfort/camfort}} for Fortran
programs and running the inference process over a corpus of 1.1
million lines of Fortran code.  Our motivation for this work was to
provide an intermediate specification language to allow scientists to
verify numerical computations.  Our evaluation showed that relatively
simple stencil comptuations are the norm, for which we can specify a
large proportion, comprising mainly reflexive region constants which
are less likely to give rise to programming errors.  However, around
10\% of stencils covered more complicated program structures for which
indexing errors are much more plausible. In the more detailed cases,
with larger specifications, the importance and impact of such
specifications grows.  We showed two examples of more complicated
stencils, for which CamFort was able to detect a significant majority
of possible indexing errors in our case studies.

@@

\bibliography{references}

>>>>

This paper considers the technical aspects of the language,
its semantics, inference, checking, and synthesis procedures.
We also evaluate our implementation on real scientific code 
used actively in research, ranging from small ($\sim$700loc) to large
($\sim$600kloc). 
 %Our case studies include the Unified Weather 
%model used by the UK Met Office~\cite{um-website} ($\approx{}600\textit{kloc}$) and other
%research-based numerical models, ranging from small to large.

@@

The product of two regions $r \texttt{*} r'$ specifies that an array
is read with neighbourhood indices drawn from the bounding box created
by the regions two regions $r$ and $r'$. For example, the following
code (defining a \emph{nine-point stencil}) has a specification given by the
product of two \texttt{centered} regions in each dimension:
%%
\begin{minted}[breakindent=2.9em]{fortran}
x = a(i, j)   + a(i-1, j)   + a(i+1, j)
y = a(i, j-1) + a(i-1, j-1) + a(i+1, j-1)
z = a(i, j+1) + a(i-1, j+1) + a(i+1, j+1)
!= stencil centered(depth=1, dim=1) * centered(depth=1, dim=2) :: a
b(i, j) = (x + y + z) / 9.0
\end{minted}
%%
This pattern is a common image convolution (for example
for edge detection). The specification ranges over the
values that flow the array subscript on the left-hand side,
and so ranges over the intermediate assignments to \term{x},
\term{y}, and \term{z}.

@@

\paragraph{Note on the design}

The names ``forward'', ``backward'' and ``centered''
are inspired by standard terminology in numerical analysis
for the shape of discretisation schemes. For example,
the standard \emph{explicit method} for approximating
PDEs is known as the \emph{Forward Time, Centered Space} (FTCS)
scheme~\cite{dawson1991finite}. For
the one-dimensional heat equation, an FTCS discretisation
provides code with the following stencil~\cite{recktenwald2004finite}:
%%
\begin{minted}{fortran}
do i=2, n-1
  u(i) = r*v(i-1) + r2*v(i) + r*v(i+1)
end do
\end{minted}
%%
where \texttt{r} and \texttt{r2} are constants.
A valid specification for this is:
%%
\begin{minted}{fortran}
!= stencil centered(depth=1, dim=1) :: v
\end{minted}
%%
Such a specification can be inferred, or can be inserted by a user
and checked against the code.

@@

Figure~\ref{fig:equations} lists the equational theory for
specifications which is defined by the binary relation $\equiv$
between region terms. The equations use abbreviations
\term{refl}, \term{fwd}, \term{bwd}, \term{cen}, and \irreflS{}
for \term{reflexive}, \term{forward}, \term{backward},
\term{centered}, and \irrefl{} respectively. Futhermore, the abbreviations include syntactic sugar
for quantifying over the abseence or presence of the \irrefl{}
attribute on region constants as a boolean. For example,
the syntactic sugar for \term{fwd} is defined:
%%
\begin{align*}
\hspace{-0.25em}
& \stenFwdSR{n}{d}{r}
\; := \; \\[-0.4em]
& \qquad \begin{cases}
\stenFwd{n}{d}{, \irrefl} & \;\;\textit{if} \;\, \neg \, r \\
\stenFwd{n}{d}{}  & \;\;\textit{if} \;\,  r
\end{cases} \\
\textit{or} \;\;
& \stenFwdS{n}{d} := \stenFwd{n}{d}{}
\end{align*}
%
and similarly for \term{bwd} and \term{cen}.

Stencil specifications in \textit{spec} are considered
equal when they have the same modifiers and $\equiv$ equates
their regions, \ie{}:
\begin{align*}
(\textit{region} \equiv \textit{region'}) 
 \Rightarrow \quad\;\; & \texttt{stencil} \; [\textit{approx},] \; [\textit{mult},] \;
\textit{region} \\[-0.4em]
\quad \equiv \; & \texttt{stencil} \; [\textit{approx},] \;
            [\textit{mult},] \; \textit{region}'
\end{align*}

The equations reveal a part of the semantics for our
specification language, which we briefly unpack.

@@

\begin{definition}
An \emph{index scheme} is a vector of size $n$ (an $n$-vector)
with values drawn from $\domainVal = \mathbb{Z} \cup \{\infty\}$.
Values in $\mathbb{Z}$ represent offsets
of a neighbourhood index (indexing
expressions of the form $i + a$ where $i$ is an induction variable
and $a$ is a constant offset, Def.\ref{def:neighbour},
p.\pageref{def:neighbour}). The additional value
$\infty$ represents any indexing behaviour--- it is a
wildcard.
Throughout $u, v, w$ range over index schemes and $u_i$ denotes
the $i^{th}$ element of $u$. We write $(\domainVal)^n$ for
the set of $n$-dimensional schemes.

Indexing schemes give an abstract
representation of index expressions in the source language.
Our model represents the meaning of stencil specifications
as indexing schemes, which explain the range of possible
indexing behaviours allowed under the specification.
The relationship between indexing schemes and source language
terms is given precisely by the partial function, \textsf{schematic}, which
maps syntactic array-index terms to indexing schemes. This
operation is used by the inference
and the checking procedures.
\end{definition}
%
\begin{definition}%[Schematic]
\label{def:schematic}
The partial function $\textsf{schematic}$ maps
source indexing terms $(e_1, .., e_n)$
to $n$-dimensional index schemes, defined:
%
\begin{align*}
\mathsf{schematic}(e_1, \ldots, e_n) & =
[\downarrow\!e_1 \ldots \downarrow\!e_n ]
\quad \textit{iff} \;\; \forall i . \downarrow\!e_i \neq \bot
\end{align*}
%
The $\downarrow$ operator is partial
 $\downarrow : \textit{expr} \rightarrow (\domainVal + \bot)$
mapping individal indexing expressions to 
an indexing scheme component, defined:
%%
\begin{align*}
\downarrow\!e
 & =  \begin{cases}
a & e \equiv i + a \; \wedge \; \mathsf{neigh}(i + a) \\
-a & e \equiv i - a \; \wedge \; \mathsf{neigh}(i - a) \\
\infty & \textit{$\mathsf{IV}(e) = \emptyset$} \\
\bot   & \textit{otherwise}
\end{cases}
\end{align*}
%%
where $\mathsf{IV}(e)$ is the set of free induction variables
in an expression, and $\neigh{}$ classifies expressions which
are constant offsets from an induction variable
(Defn.~\ref{def:neighbour}). In the third case,
if the expression is not a neighbourhood index but is not
a relative index either (\ie{}, not defined in terms
of an induction variable) then it is mapped to $\infty$, otherwise
$\downarrow\!e$ is undefined (returns $\bot$). The $\mathsf{schematic}$ function
is undefined if $\downarrow$ of any of its components $e_i$ is
undefined.

@@

@@

\begin{figure}[t]
\vspace{-0.6em}
\hspace{-0.5em}
\begin{minipage}{0.16\linewidth}
\begin{align*}
\setlength{\arraycolsep}{0em}
\begin{array}{c}
\quad \\[0em]
\begin{tikzpicture}[scale=0.8]
%\draw[step=0.5cm,lightgray,very thin] (0.5,0.5) grid (2,2);
\node at (1.25,1.22) {\textnormal{\footnotesize{0,0}}};
\draw[thick] (1,1) rectangle (1.5,1.5);
\draw[thick] (1.5,1) rectangle (2,1.5);
\draw[thick] (1,0.5) rectangle (1.5,1);
\draw[thick] (0.5,1) rectangle (1,1.5);
\draw[thick] (1,1.5) rectangle (1.5,2);
\end{tikzpicture} \\[0em]
(a)
\end{array}
\end{align*}
\end{minipage} $\rightarrow$ \begin{minipage}{0.43\linewidth}
\begin{align*}
\setlength{\arraycolsep}{0em}
\begin{array}{c}
\begin{tikzpicture}[scale=0.72]
%\draw[step=0.5cm,lightgray,very thin] (0.5,0.5) grid (2,2);
%\node at (1.25,1.22) {\textnormal{\small{0,0}}};
\draw [black, thin] (0.35,0) to [round left paren ] (0.35,2);
\draw[thick] (0.5,1) rectangle (2,1.5);
\draw[thick] (1,0.40) rectangle (1.5,0.90);
\draw[thick] (1,1.60) rectangle (1.5,2.10);
\node at (2.3,1.22) {+};
\draw[thick] (3.8,1) rectangle (4.3,1.5);
\draw[thick] (2.6,1) rectangle (3.1,1.5);
\draw[thick] (3.2,0.5) rectangle (3.7,2);
\draw [black, thin] (4.4,0) to [round right paren ] (4.4,2);
\end{tikzpicture} \\[-0.5em] (b)
\end{array}
\end{align*}
\end{minipage}$\rightarrow$ \begin{minipage}{0.25\linewidth}
\begin{align*}
\setlength{\arraycolsep}{0em}
\begin{array}{c}
\begin{tikzpicture}[scale=0.72]
%\node at (1.25,1.22) {\textnormal{\small{0,0}}};
\draw [black, thin] (0.8,0) to [round left paren ] (0.8,2);
\draw[thick] (1,0.5) rectangle (1.5,2);
\node at (1.8,1.22) {+};
\draw[thick] (2.1,1) rectangle (3.6,1.5);
\draw [black, thin] (3.7,0) to [round right paren ] (3.7,2);
%\node at (2.75,1.22) {\textnormal{\small{0,0}}};
\end{tikzpicture} \\[-0.5em] (c)
\end{array}
\end{align*}
\end{minipage}
\caption{Illustration of grouping spans in
specification inference}
\label{fig:inference-steps-informal}
\vspace{-0.8em}
\end{figure}

@@

\begin{figure}
\vspace{-0.4em}
\input{consistency.tex}
\caption{Consistency between a model and indexing schemes from a stencil computation}
\label{fig:consistency}
\vspace{-0.9em}
\end{figure}

@@

\begin{figure}[t]
  \centering
  %\subcaptionbox{\label{fig:jacobicorrect}}{\includegraphics[width=0.1\textwidth]{jacobi-correct.png}}
  %\subcaptionbox{}{\includegraphics[width=0.1\textwidth]{jacobi-incorrect1.png}}
  %\subcaptionbox{}{\includegraphics[width=0.1\textwidth]{jacobi-incorrect2.png}}
  %\subcaptionbox{}{\includegraphics[width=0.1\textwidth]{jacobi-incorrect3.png}}
  \subfigure[]{\label{fig:jacobicorrect}\includegraphics[width=0.1\textwidth]{jacobi-correct.png}}
  \subfigure[]{\includegraphics[width=0.1\textwidth]{jacobi-incorrect1.png}}
  \subfigure[]{\includegraphics[width=0.1\textwidth]{jacobi-incorrect2.png}}
  \subfigure[]{\includegraphics[width=0.1\textwidth]{jacobi-incorrect3.png}}
  \caption{Greyscale output of several perturbations of a Jacobi
    iteration program. The correct output is shown in
    \subref{fig:jacobicorrect}.}
  \label{fig:jacobi}
  \vspace{-2em}
\end{figure}

@@

There are 48 possible errors of this type of which we found only 6 were not 
detected by the specification checking. The reason is that the inferred
specification describes a family of access patterns. Some offset errors
produce a stencil computation that belongs to the same family and goes
undetected.
One of the reasons this specification can catch many offset errors is that it is
a \texttt{readOnce} specification. This prevents offset errors leading to
duplicate access patterns be caught even if the resulting set of accesses are
part of the same family.
% /um/trunk/src/atmosphere/diffusion_and_filtering/turb_smagorinsky.F90
% Tried introducing indexing errors replacing one of the indices of cx_rho_instance with -1,0,+1
% 42 cases were caught
% 6 cases were not caught
\section{Related work}
\label{sec:discussion}

@@

We presented in this work an specification language 
for the access pattern of a stencil computation. Compared to the
related work (discussed above), our language is novel in that it does
not aim to replicate indexing in the specification, but instead
provides abstract spatial combinators which capture a large number
of common patterns.

We evaluated our approach by implementing the stencil inference and
checking procedure ontop of CamFort, an open-source analysis
tool\footnotemark for Fortran
programs and running the inference process over a corpus of 1.1
million lines of Fortran code.  Our motivation for this work was to
provide an intermediate specification language to allow scientists to
verify numerical computations.  Our evaluation showed that relatively
simple stencil comptuations are the norm, for which we can specify a
large proportion, comprising mainly reflexive region constants which
are less likely to give rise to programming errors.  However, around
10\% of stencils covered more complicated program structures for which
indexing errors are much more plausible. In the more detailed cases,
with larger specifications, the importance and impact of such
specifications grows.  We showed two examples of more complicated
stencils, for which CamFort was able to detect a significant majority
of possible indexing errors in our case studies.

@@

\footnotetext{\url{https://github.com/camfort/camfort}}
\bibliography{references}
